Mechanized Reasoning about a Capability Machine

### 2019-10-17 prisc-2020/paper.tex

\begin{itemize}
\item we define the operational semantics of the CM
\item we prove basic hoare triples for each of the atomic instructions
  of the CM (i.e., for load, store, etc.)
\item non-trivial
  \begin{itemize}
  \item while Iris is a framework and supports many languages, it is
    geared towards models of higher-level languages which abstract from
    program counters and the fact that programs are stored in memory.
    -- here our low-level machine model includes registers, in particular
    the program counter register, and instructions are stored in memory.
   \item hence we 
  \end{itemize}
\end{itemize}

@@

\section{Logical Relation}
\begin{figure*}[ht]
	\begin{minipage}{\textwidth}
	\begin{align*}
		\mathcal{E}\interp{W}{pc} \triangleq&~\forall r, \mathcal{R}(W)(r) ~*~\textsf{context}(W)(r[\textsf{\small PC}:=pc])\\
		&\sep~\textsc{WP}~\textsf{Seq (Instr Executable)}~\{ v, v = HaltedV \implies \exists W' r', W' \sqsubseteq_{priv} W * \textsf{context}(W')(r')\}
	\end{align*}
	\end{minipage}
	\caption{Logical Relation for Expressions}
	\label{fig:expr}
\end{figure*}

>>>>

\begin{itemize}
\item we define the operational semantics of the CM
\item we prove basic hoare triples for each of the atomic instructions
  of the CM (i.e., for load, store, etc.)
\item non-trivial
  \begin{itemize}
  \item while Iris is a framework and supports many languages, it is
    geared towards models of higher-level languages which abstract from
    program counters and the fact that programs are stored in memory.
    -- here our low-level machine model includes registers, in particular
    the program counter register, and instructions are stored in memory.
  \item to capture the semantics of the CM in the Iris framework, 
    we introduce an abstract notion of instruction, whose
    operational meaning is to execute the next instruction the program counter
    points to, and abstract notions of values, failed and halted.
  \item for each machine instruction, we can then prove a hoare triple
    which expresses the pre- and post-conditions for executing the instruction
  \end{itemize}
\end{itemize}

@@

\section{Logical Relation}

\begin{itemize}
\item LS: worlds contained all invariants, both on local state and ``standard islands'' for capabilities
\item now, simplified, world only contains sts's for local state, whereas the conditions on capabilities are captured by the permission of the points-to connective
\end{itemize}

\begin{figure*}[ht]
	\begin{minipage}{\textwidth}
	\begin{align*}
		\mathcal{E}\interp{W}{pc} \triangleq&~\forall r, \mathcal{R}(W)(r) ~*~\textsf{context}(W)(r[\textsf{\small PC}:=pc])\\
		&\sep~\textsc{WP}~\textsf{Seq (Instr Executable)}~\{ v, v = HaltedV \implies \exists W' r', W' \sqsubseteq_{priv} W * \textsf{context}(W')(r')\}
	\end{align*}
	\end{minipage}
	\caption{Logical Relation for Expressions}
	\label{fig:expr}
\end{figure*}
